%-------------------------
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Arnav Surve} \\ \vspace{0pt}
    \vspace{5pt}
    \small 916-472-9444 $|$ \href{mailto:arnav@surve.dev}{\underline{arnav@surve.dev}} $|$ 
    \href{https://linkedin.com/in/arnavsurve/}{\underline{linkedin.com/in/arnavsurve}} $|$
    \href{https://github.com/arnavsurve}{\underline{github.com/arnavsurve}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California State University - Sacramento}{Sacramento, CA}
      {Bachelor of Science, Computer Science}{Aug. 2024 -- May 2026}
      \resumeProjectHeading
      {CSC 20 - Java OOP, CSC 35 - Computer Architecture}{}

    \vspace{3pt}

    \resumeSubheading
      {Purdue University}{West Lafayette, IN}
      {Bachelor of Science, Cybersecurity -- Dean's List, Fall 2023}{Aug. 2022 -- May 2024}
      \resumeProjectHeading
      {CNIT 27000 \& 27100 - Cybersecurity Fundamentals I \& II, CNIT 24200 - System Administration}{}
  \resumeSubHeadingListEnd


% -----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{taskman} $|$ \emph{Go, PostgreSQL}}{Aug 2024 - Current}
        \resumeItemListStart
          \resumeItem{}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{LastFM-crawl} $|$ \emph{Python, Flask, AWS Lambda, Docker}}{July 2024}
        \resumeItemListStart
          \resumeItem{Developed a wrapper for the Last.fm API use as a modular way to embed Last.fm stats in my website or application.}
          \resumeItem{Implemented API endpoints to serve JSON data (e.g. listening history, followers/following, and aggregated daily/monthly/yearly listening stats).}
          \resumeItem{Containerized using Docker and created a CI/CD pipeline with Zappa for seamless testing and deployment.}
          \resumeItem{Deployed to AWS Lambda for serverless endpoint access, mitigating \textbf{$\sim$\$15} in monthly costs compared to EC2.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{-12pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IT Infrastructure Intern}{June 2024 -- Aug. 2024}
      {MITER Brands -- Milgard Manufacturing}{Tacoma, WA}
      \resumeItemListStart
        \resumeItem{Analyzed IT server, application, and network monitoring landscape.}
        \resumeItem{Composed a proposal to optimize monitoring alerts flow for greater scalability and quicker incident resolution, reducing average inbox volumes by \textbf{$\sim$60\%.}}
        \resumeItem{Developed 5 Site24x7 monitors to track latency metrics for Infor Cloud REST API endpoints.}
        \resumeItem{Overhauled Site24x7 monitor and alert groups, escalation policies, and alert thresholds to mitigate tech debt and improve efficiency by \textbf{$\sim$20\%.}}
        \resumeItem{Automated compliance audits for Active Directory controlled accounts using PowerShell scripting.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Undergraduate Researcher}{May 2024 -- Aug. 2024}
      {NASA California Space Grant Consortium}{Sacramento, CA}
      \resumeItemListStart
      \resumeItem{Developed unsupervised classification models employing K-Means clustering and agglomerative clustering for volcanic activity prediction using infrasound frequencies, utilizing datasets from Boise State University Scholarworks with a maximum silhouette score of \textbf{0.47}.}
        \resumeItem{Constructed an infrasound sensor array and monitor using Amphenol Board Mount Sensors and Raspberry Pi.}
    \resumeItemListEnd

    \resumeSubheading
      {Backend Developer}{Aug. 2022 -- May 2023}
      {Purdue University Office of Engagement}{West Lafayette, IN}
      \resumeItemListStart
      \resumeItem{Worked in a 10 person team using Agile methodology to develop a web application to enable research grant applications.}
      \resumeItem{Developed 7 REST API endpoints using Express.js to enable CRUD functionality.}
      \resumeItem{Implemented federated authentication using Purdue University Single Sign-On.}
        \resumeItem{Architected an ORM database to handle user PII and grant applications using PostgreSQL.}
        \resumeItem{Utilized Docker for containerization and ease in deployment of backend services.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {IT Support Desk Intern}{March 2021 -- Aug. 2021}
    %   {California Department of Technology}{Sacramento, CA}
    %   \resumeItemListStart
    %     \resumeItem{Imaged and deployed 60 desktop computers with Windows 10 and Office 365}
    %     \resumeItem{\textbf{Optimized PC cataloging and inventory management by $\sim$30\%} using Excel and Powershell}
    %     \resumeItem{Configured 30 cubicles with network and power connections as hotels in preparation for remote work following COVID-19}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd


%
%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, SQL, Go, Bash, \LaTeX, Javascript, HTML/CSS} \\
     \textbf{Frameworks}{: Agile, PostgreSQL, Svelte, Node.js, Express.jss} \\
     \textbf{Tools}{: Git, Vim, AWS (S3, EC2, Lambda), Bash, Docker, Jupyter Notebooks} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, InfraPy, SciKit-Learn}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
